---
title-block: none
format:
  html:
    toc: true
    embed-resources: true
    self-contained: true
params:
  meta: NULL
  input_dir: ./
  input_filename: NULL
  artifact_dir: NULL
  cpus: 1
  input_ids: NULL
  input_files: NULL
  input_file_count: 0
---

# Provenance report

This report was rendered by `nf-core/provenancereport` from all files listed in the input samplesheet.

```{r setup}
#| include: false
report_id <- if (!is.null(params$meta$id)) params$meta$id else "report"
artifact_dir <- params$artifact_dir
if (is.null(artifact_dir) || artifact_dir == "") {
    artifact_dir <- "artifacts"
}
dir.create(artifact_dir, showWarnings = FALSE, recursive = TRUE)
split_param <- function(value) {
    if (is.null(value) || !nzchar(value)) {
        return(character())
    }
    strsplit(value, ",", fixed = TRUE)[[1]]
}
input_ids <- split_param(params$meta$input_ids)
input_files <- split_param(params$meta$input_files)
input_table <- data.frame(
    id = input_ids,
    file = input_files,
    stringsAsFactors = FALSE
)
write.table(
    input_table,
    file = file.path(artifact_dir, paste0(report_id, "_input_files.tsv")),
    sep = "\t",
    row.names = FALSE,
    quote = FALSE
)
writeLines(
    c(
        paste0("report_id: ", report_id),
        paste0("input_file_count: ", length(input_files))
    ),
    con = file.path(artifact_dir, paste0(report_id, "_summary.txt"))
)
```

## Report metadata

- Report id: `r report_id`
- Input file count: `r length(input_files)`
- CPUs available to the report task: `r params$cpus`

## Input files

The samplesheet `id` values are provided through `params$meta$input_ids`, and staged filenames are provided through `params$meta$input_files` in the same order.

```{r input-files}
#| echo: false
if (length(input_files) == 0) {
    cat("No input files were supplied.\n")
} else {
    knitr::kable(input_table, col.names = c("Input id", "Staged file"))
}
```

## Artifacts

This notebook writes a small TSV and text summary into `params$artifact_dir`. Custom notebooks can use the same parameter to write tables, images, or other report artifacts for publication by the pipeline.
